Java Sorting Algorithms Comparison

### 2015-02-18 Programming Project B/paper.tex
modified insertion sort, added partial merge sort

%% Title Page
\title{Java Sorting Algorithms Run-Time Analysis}
\author{Preston Stosur-Bassett}
\date{February 23, 2015}
\maketitle

@@

%% BEGIN MOTIVATION
\section{Motivation}

%% END MOTIVATION

%% BEGIN BACKGROUND
\section{Background}

%% END BACKGROUND

@@

%% BEGIN REFERENCES
%% \section*{References}

\nocite{*}
\bibligraphystyle{IEEEtran}
\bibliography{}

>>>>

%% Title Page
\title{Java Sorting Algorithms Comparison}
\author{Preston Stosur-Bassett}
\date{February 23, 2015}
\maketitle

@@

%% BEGIN MOTIVATION
\section{Motivation}
In order to show how an algorithm might run on a given set of hardware, and how the algorithm will perform when given large amounts of data, algorithms are analysed. Sorting algorithms sort data into a natural order. By analysing sorting algorithms, the fastest algorithm for a given problem can be determined. 
%% END MOTIVATION

%% BEGIN BACKGROUND
\section{Background}
A sorting algorithm is used to sort data with a natural order. One such sorting algorithm is insertion sort, which sorts by iterating through a list of data, taking the current position, and repositioning it into a more appropriate place in the list. %% Merge sort and Heap Sort
%% END BACKGROUND

@@

%% BEGIN REFERENCES
 \section*{References}

%%\nocite{*}
%%\bibligraphystyle{IEEEtran}
%%\bibliography{}
